---
title: "Futures Trades"
---

<link rel="stylesheet" type="text/css" href="https://cdn.datatables.net/1.10.24/css/jquery.dataTables.css">

```{=html}
<script type="text/javascript" charset="utf8" src="https://code.jquery.com/jquery-3.5.1.min.js"></script>
```
```{=html}
<script type="text/javascript" charset="utf8" src="https://cdn.datatables.net/1.10.24/js/jquery.dataTables.js"></script>
```
<https://forms.gle/PscmhTrE13roMsw37>

## Top


```{r setup}
#| include: false

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(googlesheets4)
library(tidyr)
library(kableExtra)
library(hms)
barchart_key <- Sys.getenv("BARCHART_Key")
json_key_path <- Sys.getenv("GOOGLE_SHEETS_JSON")
gs4_auth(path = json_key_path)
```

```{r}
my_sheet <- read_sheet("1y1Kv8qzbVwlKQoZNc7k4EiYykN7U55ORQll7hOlcA9k") %>%
  mutate(`Partial Email` = substr(`Email Address`, 1,4)) %>% 
  select(c(1, 29, 10, 13, 15, 16, 19, 20 ))

new_column_names <-  c("K Corn", "Z Corn", "K Soybean", "X Soybean", "K Wheat", "Z Wheat")
colnames(my_sheet)[3:8] <- new_column_names

# If trade before the close you get same day close price. If after the close, you get next day close price. 
my_sheet <- my_sheet %>%
  rowwise() %>%
  mutate(
    Date = case_when(
      wday(Timestamp) %in% 2:6 & (hour(Timestamp) < 14 || (hour(Timestamp) == 14 && minute(Timestamp) < 20)) ~ as.Date(Timestamp),
      wday(Timestamp) %in% 2:6 & (hour(Timestamp) > 14 || (hour(Timestamp) == 14 && minute(Timestamp) >= 20)) ~ as.Date(Timestamp) + days(1))) %>%
  mutate(Date = case_when(wday(Date) == 1 ~ as.Date(Date) + days(1),  # From Sunday to Monday
      wday(Date) == 7 ~ as.Date(Date) + days(2),   # From Saturday to Monday
      TRUE ~ as.Date(Date)
    )
  )

my_sheet <- my_sheet %>% select(c(1,2, 9, 3:8))

```

```{r}

DATA1 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZCK24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2)) 

DATA2 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZSK24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2))

DATA3 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZWK24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2))

DATA <- rbind(DATA1, DATA2, DATA3)

DATAK <- DATA %>% mutate (closeSpot = case_when(symbol == "ZC" ~ close + (.05*exp(close/100 - 450/100) - 25/100)*100,
                                       symbol == "ZS" ~ close + (.05*exp(close/100 - 1260/100) - 50/100)*100,
                                       symbol == "ZW" ~ close + (.05*exp(close/100 - 600/100) - 25/100)*100))

todayPricesK <- DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close) %>% arrange(Date) %>% last()
###########
# New Crop
DATA1 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZCZ24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2)) 

DATA2 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZSX24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2))

DATA3 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZWN24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2))

DATA <- rbind(DATA1, DATA2, DATA3)

DATANew <- DATA %>% mutate (closeSpot = case_when(symbol == "ZC" ~ close + (.05*exp(close/100 - 450/100) - 25/100)*100,
                                       symbol == "ZS" ~ close + (.05*exp(close/100 - 1260/100) - 50/100)*100,
                                       symbol == "ZW" ~ close + (.05*exp(close/100 - 600/100) - 25/100)*100))
todayPricesNew <- DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close) %>% arrange(Date) %>% last()

```

# Corn

## All Trades in May Corn
  
```{r}

tableZCK <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,4,10))

colnames(tableZCK) <- c('Partial Email', "Date", "K Corn Trade in Bushels", "Price of Trade in K Corn")

tableZCK %>% 
 knitr::kable("html", table.attr = "id='myTableZCK'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZCK').DataTable();
  });
  </script>
```


## Net Profit/Loss in May Corn

This number includes both closed trades and open trades. Open positions are found in the Net Position column. Net Position is in bushels, PNL is in dollars. 

```{r}

# This table calculates overall PNL
tableZCK <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,4,10)) %>% 
  summarize(NetPos = sum(`K Corn`), PNL = (-sum(`K Corn`*ZC.x) + (NetPos)*todayPricesK$ZC)/100, "Current Price K Corn" = todayPricesK$ZC)

tableZCK$PNL <- round(tableZCK$PNL, 2)
colnames(tableZCK) <- c("Partial Email", "Net Position", "PNL", "Current Price K Corn")

tableZCK  %>% 
 knitr::kable("html", table.attr = "id='myTableZCKPNL'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZCKPNL').DataTable();
  });
  </script>
```
  
## All Trades in Dec Corn
  
```{r}

tableZCZ <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,5,13))

colnames(tableZCZ) <- c('Partial Email', "Date", "Z Corn Trade in Bushels", "Price of Trade in Z Corn")

tableZCZ   %>% 
 knitr::kable("html", table.attr = "id='myTableZCZ'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZCZ').DataTable();
  });
  </script>
```

## Net Profit/Loss in December Corn

This number includes both closed trades and open trades. Open positions are found in the Net Position column. Net Position is in bushels, PNL is in dollars. 

```{r}

# This table calculates overall PNL
tableZCZ <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,5,13)) %>% 
  summarize(NetPos = sum(`Z Corn`), PNL = (-sum(`Z Corn`*ZC.y) + (NetPos)*todayPricesNew$ZC)/100, "Current Price Z Corn" = todayPricesNew$ZC)

tableZCZ$PNL <- round(tableZCZ$PNL, 2)
colnames(tableZCZ) <- c("Partial Email", "Net Position", "PNL", "Current Price Z Corn")

tableZCZ   %>% 
 knitr::kable("html", table.attr = "id='myTableZCZPNL'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZCZPNL').DataTable();
  });
  </script>
```

# Soybeans
## All Trades in May Soybeans
  
```{r}

tableZSK <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,6,11))

colnames(tableZSK) <- c('Partial Email', "Date", "K Soybean Trade in Bushels", "Price of Trade in K Soybean")

tableZSK %>% 
 knitr::kable("html", table.attr = "id='myTableZSK'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZSK').DataTable();
  });
  </script>
```


## Net Profit/Loss in May Soybeans

This number includes both closed trades and open trades. Open positions are found in the Net Position column. Net Position is in bushels, PNL is in dollars. 

```{r}

# This table calculates overall PNL
tableZSK <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,6,11)) %>% 
  summarize(NetPos = sum(`K Soybean`), PNL = (-sum(`K Soybean`*ZS.x) + (NetPos)*todayPricesK$ZS)/100, "Current Price K Soybeans" = todayPricesK$ZS)

tableZSK$PNL <- round(tableZSK$PNL, 2)
colnames(tableZSK) <- c("Partial Email", "Net Position", "PNL", "Current Price K Sobyean")

tableZSK  %>% 
 knitr::kable("html", table.attr = "id='myTableZSKPNL'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZSKPNL').DataTable();
  });
  </script>
```

## All Trades in December Soybeans
  
```{r}

tableZSX <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,7,14))

colnames(tableZSX) <- c('Partial Email', "Date", "X Soybean Trade in Bushels", "Price of Trade in X Soybean")

tableZSX %>% 
 knitr::kable("html", table.attr = "id='myTableZSX'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZSX').DataTable();
  });
  </script>
```

## Net Profit/Loss in December Soybeans

This number includes both closed trades and open trades. Open positions are found in the Net Position column. Net Position is in bushels, PNL is in dollars. 

```{r}

# This table calculates overall PNL
tableZSX <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,7,14)) %>% 
  summarize(NetPos = sum(`X Soybean`), PNL = (-sum(`X Soybean`*ZS.y) + (NetPos)*todayPricesNew$ZS)/100, "Current Price X Soybeans" = todayPricesNew$ZS)

tableZSX$PNL <- round(tableZSX$PNL, 2)
colnames(tableZSX) <- c("Partial Email", "Net Position", "PNL", "Current Price X Sobyean")

tableZSX  %>% 
 knitr::kable("html", table.attr = "id='myTableZSXPNL'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZSXPNL').DataTable();
  });
  </script>
```

# Wheat

## All Trades in May Wheat
  
```{r}

tableZWK <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,8,12))

colnames(tableZWK) <- c('Partial Email', "Date", "K Wheat Trade in Bushels", "Price of Trade in K Wheat")

tableZWK %>% 
 knitr::kable("html", table.attr = "id='myTableZWK'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZWK').DataTable();
  });
  </script>
```


## Net Profit/Loss in May Wheat

This number includes both closed trades and open trades. Open positions are found in the Net Position column. Net Position is in bushels, PNL is in dollars. 

```{r}

# This table calculates overall PNL
tableZWK <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,8,12)) %>% 
  summarize(NetPos = sum(`K Wheat`), PNL = (-sum(`K Wheat`*ZW.x) + (NetPos)*todayPricesK$ZW)/100, "Current Price K Wheat" = todayPricesK$ZW)

tableZWK$PNL <- round(tableZWK$PNL, 2)
colnames(tableZWK) <- c("Partial Email", "Net Position", "PNL", "Current Price K Wheat")

tableZWK  %>% 
 knitr::kable("html", table.attr = "id='myTableZWKPNL'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZWKPNL').DataTable();
  });
  </script>
```


## All Trades in December Wheat
  
```{r}

tableZWZ <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,9,15))

colnames(tableZWZ) <- c('Partial Email', "Date", "Z Wheat Trade in Bushels", "Price of Trade in Z Wheat")

tableZWZ %>% 
 knitr::kable("html", table.attr = "id='myTableZWZ'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZWZ').DataTable();
  });
  </script>
```


## Net Profit/Loss in December Wheat

This number includes both closed trades and open trades. Open positions are found in the Net Position column. Net Position is in bushels, PNL is in dollars. 

```{r}

# This table calculates overall PNL
tableZWZ <- left_join(my_sheet,  
          DATAK %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>% 
  left_join(DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close), 
          #rbind(DATA %>% pivot_wider(names_from = symbol, values_from = close),
          #     tibble(Date = as.Date("2024-01-11"), ZC = 461.00, ZS = 1230, ZW = 612)), #For testing only DELETE and uncomment line above!
          by =  "Date") %>%
  group_by(`Partial Email`) %>%
  arrange(`Partial Email`) %>% 
  mutate(TradeDate = Date) %>%  
  mutate_if(is.numeric, ~ifelse(is.na(.), 0, .)) %>% # replace na's with zeros becasue it kills cumsum
  select(c(2,3,9,15)) %>% 
  summarize(NetPos = sum(`Z Wheat`), PNL = (-sum(`Z Wheat`*ZW.y) + (NetPos)*todayPricesNew$ZW)/100, "Current Price Z Wheat" = todayPricesNew$ZW)

tableZWZ$PNL <- round(tableZWZ$PNL, 2)
colnames(tableZWZ) <- c("Partial Email", "Net Position", "PNL", "Current Price Z Wheat")

tableZWZ  %>% 
 knitr::kable("html", table.attr = "id='myTableZWZPNL'") 

```


```{=html}
<script>
  $(document).ready( function () {
      $('#myTableZWZPNL').DataTable();
  });
  </script>
```

# Summary of PNL for All Contracts 

```{r}
summaryPNL <- tableZCK %>% 
  inner_join( tableZCZ, by = "Partial Email") %>% 
  select(c("Partial Email", PNL.x, PNL.y)) %>% 
  inner_join(tableZSK, by = "Partial Email") %>% 
  inner_join(tableZSX, by = "Partial Email") %>% 
  select(c("Partial Email", PNL.x, PNL.y, PNL.x.x, PNL.y.y)) %>% 
  inner_join(tableZWK, by = "Partial Email") %>% 
  inner_join(tableZWZ, by = "Partial Email") %>% 
  select(c("Partial Email", PNL.x, PNL.y, PNL.x.x, PNL.y.y, PNL.x.x.x, PNL.y.y.y)) %>% 
   rename(
    `PNL May Corn` = PNL.x, 
    `PNL Dec Corn` = PNL.y, 
    `PNL May Soybean` = PNL.x.x, 
    `PNL November Soybean` = PNL.y.y,
    `PNL May Wheat` = PNL.x.x.x,
    `PNL December Wheat` = PNL.y.y.y
  ) %>% 
  mutate(`Total PNL` = rowSums(select(., -`Partial Email`), na.rm = TRUE))

write.csv(summaryPNL, file = "summaryPNL.csv")

summaryPNL %>%
 knitr::kable("html", table.attr = "id='summaryPNL'") 
```

```{=html}
<script>
  $(document).ready( function () {
      $('#summaryPNL').DataTable();
  });
  </script>
```
