---
title: "Expected Net Profit"
---

```{r setup}
#| include: false

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(googlesheets4)
library(tidyr)
library(kableExtra)
library(hms)
library(scales)
barchart_key <- Sys.getenv("BARCHART_Key")

# Make sure all expected bushels and expected prices are are set right during game versus close game. 

```

<link rel="stylesheet" type="text/css" href="https://cdn.datatables.net/1.10.24/css/jquery.dataTables.css">

```{=html}
<script type="text/javascript" charset="utf8" src="https://code.jquery.com/jquery-3.5.1.min.js"></script>
```
```{=html}
<script type="text/javascript" charset="utf8" src="https://cdn.datatables.net/1.10.24/js/jquery.dataTables.js"></script>
```
```{r}
###########
# Get futures prices  
# New Crop
DATA1 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZCZ24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2)) 

DATA2 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZSX24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2))

DATA3 <- read.csv(url(paste0("http://ondemand.websol.barchart.com/getHistory.csv?apikey=", barchart_key ,"&symbol=ZWN24&type=daily&startDate=20190101"))) %>%
  mutate(Date = as.Date(tradingDay)) %>% 
  select(symbol, Date, close) %>%
  mutate(symbol = substr(symbol, 1,2))

DATA <- rbind(DATA1, DATA2, DATA3)

DATANew <- DATA %>% mutate (closeSpot = case_when(symbol == "ZC" ~ close + (.05*exp(close/100 - 450/100) - 25/100)*100,
                                       symbol == "ZS" ~ close + (.05*exp(close/100 - 1260/100) - 50/100)*100,
                                       symbol == "ZW" ~ close + (.05*exp(close/100 - 600/100) - 25/100)*100))
todayPricesNew <- DATANew %>% select(-closeSpot) %>% pivot_wider(names_from = symbol, values_from = close) %>% arrange(Date) %>% last()
```

# Game Closed!

### Latest New Crop Futures Prices and Yield Realizations

These are used to calculate revenue from spot sales at 2024 harvest.

```{r}
# change to todayPriceNew to open game again
game_draw <- read.csv('game_draw.csv')
select(game_draw , c(2,6:12)) %>%
#todayPricesNew %>%  
 knitr::kable()



```

# Components of Total Revenue

## Futures Trades Profit and Loss

```{r}
# Futures trades PNL
futuresPNL <- read.csv("summaryPNL.csv")
futuresPNL %>% 
  mutate(across(where(is.numeric), ~comma(., accuracy = 1))) %>%
 knitr::kable("html", table.attr = "id='futuresPNL'") 

```

```{=html}
<script>
  $(document).ready( function () {
      $('#futuresPNL').DataTable();
  });
  </script>
```
## Revenue from Spot and Forward Sales of 2023 Bushels and Forward Sales of 2024 Bushels

Figures are rounded to nearest dollar.

```{r}
# Spot/forward Sales revanue
corn_spot_forward_Revenue <- read.csv("Corn_spotforward_sales.csv") %>% 
  mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  mutate(Cspot23 = X23.Corn.Spot.Sales*X23.Corn.Spot.Ave.Price,
         Cforward23 = X23.Corn.Forward.Sales*X23.Corn.Forward.Ave.Price,
         Cforward24 = X24.Corn.Forward.Sales*X24.Corn.Forward.Ave.Price) %>% 
  select(c(2, 9:11))


sobyean_spot_forward_Revenue <- read.csv("Soybean_spotforward_sales.csv") %>% 
   mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  mutate(Sspot23 = X23.Soybean.Spot.Sales*X23.Soybean.Spot.Ave.Price,
         Sforward23 = X23.Soybean.Forward.Sales*X23.Soybean.Forward.Ave.Price,
         Sforward24 = X24.Soybean.Forward.Sales*X24.Soybean.Forward.Ave.Price) %>% 
  select(c(2, 9:11))

wheat_spot_forward_Revenue <- read.csv("Wheat_forward_sales.csv") %>% 
   mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  mutate(Wforward24 = X24.Wheat.Forward.Sales*X24.Wheat.Forward.Ave.Price) %>% 
  select(c(2, 5))


# Revenue in dollars from 23 spot and forward sales, plus 24 forward contracts
spot_forward_rev <- corn_spot_forward_Revenue %>% 
   mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  inner_join(sobyean_spot_forward_Revenue, by = "Partial.Email") %>% 
  inner_join(wheat_spot_forward_Revenue, by = "Partial.Email")

spot_forward_rev  %>% 
  mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  mutate(across(where(is.numeric), ~comma(round(., 0), accuracy = 1))) %>%
  knitr::kable("html", table.attr = "id='spotforward'") 

```

```{=html}
<script>
  $(document).ready( function () {
      $('#spotforward').DataTable();
  });
  </script>
```

```{r}
## Expected Bushels Based on Acreage Choices for Different Crops and Practices
# Acreage and Expected Yields
expected_yields <- data.frame(cc = 208, rc = 221, rb = 67, w = 93, dcb = 47)

# Gross expected bushels (separate off what has been contracted to multiply that remainder by expected spot at harvest)
bushels <- read.csv("acreage.csv") %>% 
  mutate(CCorn_Expected_Bushels = Continuous.Corn*expected_yields$cc,
         RCorn_Expected_Bushels = Rotational.Corn*expected_yields$rc,
         RSoybean_Expected_Bushels = Soybean*expected_yields$rb,
         Wheat_Expected_Bushels = Wheat*expected_yields$w,
         DSoybeans_Expected_Bushels = Double.Crop.Soybean*expected_yields$dcb) %>% 
  select(c(3, 9:13))

# Realized bushels to be used in spot calculations and insurance payments later
# note that we left the names 'expected_bushels' for convenience, when used in bushels_gameclose below it is realized not expected bushels

bushels_gameclose <- read.csv("acreage.csv") %>% 
  mutate(CCorn_Expected_Bushels = Continuous.Corn*game_draw$Yield_Corn*expected_yields$cc/expected_yields$rc,
         RCorn_Expected_Bushels = Rotational.Corn*game_draw$Yield_Corn,
         RSoybean_Expected_Bushels = Soybean*game_draw$Yield_Soybean,
         Wheat_Expected_Bushels = Wheat*game_draw$Yield_Wheat,
         DSoybeans_Expected_Bushels = Double.Crop.Soybean*game_draw$Yield_Soybean*expected_yields$dcb/expected_yields$rb) %>% 
  select(c(3, 9:13))

# bushels %>% 
#   kable("html", escape = FALSE) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## Revenue from New Crop Spot Sales



### Revenue for Spot Sales at 2024 Harvest

Expected bushels available for spot sales at harvest are total expected bushels minus any bushels forward contracted. E.g., Expected Bushels - 2024 Forward Contracted Bushels. Then, this number is multiplied by the current new crop futures prices to get expected revenue from spot sales at 2024 harvest.



```{r}
# Calculate expected revenue from spot sales at 2024 harvest
new_crop_spot <- bushels %>% inner_join( read.csv("Corn_spotforward_sales.csv") %>% select(c(2, 7)), by = "Partial.Email") %>% 
  inner_join(read.csv("Soybean_spotforward_sales.csv") %>% select(2, 7), by = "Partial.Email") %>% 
  inner_join( read.csv("Wheat_forward_sales.csv") %>% select(2,3), by = "Partial.Email") %>%
  mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  mutate(SpotCorn_Bushels = CCorn_Expected_Bushels + RCorn_Expected_Bushels - X24.Corn.Forward.Sales,
         SpotSoy_Bushels = RSoybean_Expected_Bushels + DSoybeans_Expected_Bushels - X24.Soybean.Forward.Sales,
         SpotWheat_Bushels = Wheat_Expected_Bushels - X24.Wheat.Forward.Sales) %>% 
  select(c(1, 10:12)) %>% 
  mutate(Exp_New_Corn_Rev = SpotCorn_Bushels*todayPricesNew$ZC/100,
         Exp_New_Soy_Rev = SpotSoy_Bushels*todayPricesNew$ZS/100,
         Exp_New_Wheat_Rev = SpotWheat_Bushels*todayPricesNew$ZW/100) %>% 
  select(c(1, 5:7))

# new_crop_spot   %>% 
#   mutate(across(where(is.numeric), ~comma(round(., 0), accuracy = 1))) %>%
#  knitr::kable("html", table.attr = "id='newcropspot'") 


# Use this to close the game/comment out if not time to close game

new_crop_spot <- bushels_gameclose %>% inner_join( read.csv("Corn_spotforward_sales.csv") %>% select(c(2, 7)), by = "Partial.Email") %>% 
  inner_join(read.csv("Soybean_spotforward_sales.csv") %>% select(2, 7), by = "Partial.Email") %>% 
  inner_join( read.csv("Wheat_forward_sales.csv") %>% select(2,3), by = "Partial.Email") %>%
  mutate(across(everything(), ~replace(., is.na(.), 0))) %>% 
  mutate(SpotCorn_Bushels = CCorn_Expected_Bushels + RCorn_Expected_Bushels - X24.Corn.Forward.Sales,
         SpotSoy_Bushels = RSoybean_Expected_Bushels + DSoybeans_Expected_Bushels - X24.Soybean.Forward.Sales,
         SpotWheat_Bushels = Wheat_Expected_Bushels - X24.Wheat.Forward.Sales) %>% 
  select(c(1, 10:12)) %>% 
  mutate(Exp_New_Corn_Rev = SpotCorn_Bushels*game_draw$Price_Corn,
         Exp_New_Soy_Rev = SpotSoy_Bushels*game_draw$Price_Soybean,
         Exp_New_Wheat_Rev = SpotWheat_Bushels*game_draw$Price_Wheat) %>% 
  select(c(1, 5:7))

new_crop_spot   %>% 
  mutate(across(where(is.numeric), ~comma(round(., 0), accuracy = 1))) %>%
 knitr::kable("html", table.attr = "id='newcropspot'") 

```

```{=html}
<script>
  $(document).ready( function () {
      $('#newcropspot').DataTable();
  });
  </script>
```

## Crop Insurance Indemnity Payment



```{r}
ci_corn <- 4.66
ci_soy <- 11.55



# Per Acre Insurance Payouts



# 90% was only coverage option
CCorn_CI_Payment <- max(0, max(ci_corn, game_draw$Price_Corn)*expected_yields$cc*.9 - game_draw$Price_Corn*game_draw$Yield_Corn*expected_yields$cc/expected_yields$rc )

RCorn_CI_Payment <- max(0, max(ci_corn, game_draw$Price_Corn)*expected_yields$rc*.9 - game_draw$Price_Corn*game_draw$Yield_Corn )

RSoybean_CI_Payment <- max(0, max(ci_soy, game_draw$Price_Soybean)*expected_yields$rb*.9 - game_draw$Price_Soybean*game_draw$Yield_Soybean )

# Number of Insured Acres Chosen by participant
prop <- read.csv('prop_insured_acreage.csv') %>% select(-c(X, Timestamp))  
acres <- read.csv('acreage.csv') %>% select(-c(X, Timestamp)) 
ins_acres <- left_join(prop, acres, by = 'Partial.Email')

ins_acres <- ins_acres %>%
  mutate(
    InsuredAcres_ContinuousCorn = Continuous.Corn.x/100 * Continuous.Corn.y,
    InsuredAcres_RotationalCorn = Rotational.Corn.x/100 * Rotational.Corn.y,
    InsuredAcres_Soybean = Soybean.x/100 * Soybean.y,
    InsuredAcres_Wheat = Wheat.x/100 * Wheat.y
  ) %>%
  select(Partial.Email, 
         InsuredAcres_ContinuousCorn, 
         
         
         InsuredAcres_RotationalCorn, 
         InsuredAcres_Soybean, 
         InsuredAcres_Wheat)  %>% 
  mutate(across(everything(), ~replace(., is.na(.), 0)))


Insurance_Payments <- ins_acres %>% 
  mutate(
    # Calculating CI payments based on insured acres and pre-defined per acre payment logic
    Corn_CI_Payment = InsuredAcres_ContinuousCorn * CCorn_CI_Payment,
    RCorn_CI_Payment = InsuredAcres_RotationalCorn * RCorn_CI_Payment,
    RSoybean_CI_Payment = InsuredAcres_Soybean * RSoybean_CI_Payment
  ) %>% 
  select(-(2:5))
  
 Insurance_Payments %>%
 knitr::kable("html", table.attr = "id='ins_pmt'") 
```

```{=html}
<script>
  $(document).ready( function () {
      $('#newcropspot').DataTable();
  });
  </script>
```

# Aggregating all Revenue Sources

```{r}
total <- futuresPNL %>% 
  inner_join(spot_forward_rev, by = "Partial.Email") %>%
  inner_join(new_crop_spot, by = "Partial.Email") %>% 
  inner_join(Insurance_Payments, by = 'Partial.Email') %>% 
  mutate(`Total PNL` = rowSums(select(., -"Partial.Email"), na.rm = TRUE))

total %>%
  select(c(2, 23)) %>% 
  mutate(across(where(is.numeric), ~comma(round(., 0), accuracy = 1))) %>%
 knitr::kable("html", table.attr = "id='allrev'") 

```

```{=html}
<script>
  $(document).ready( function () {
      $('#allrev').DataTable();
  });
  </script>
```
## Aggregate Revenue Detailed View

```{r}
total  %>% 
  mutate(across(where(is.numeric), ~comma(round(., 0), accuracy = 1))) %>%
 knitr::kable("html", table.attr = "id='allrevdetail'") 

```

```{=html}
<script>
  $(document).ready( function () {
      $('#allrevdetail').DataTable();
  });
  </script>
```
